Flabby and injective objects in toposes

### 2019-07-31 paper-flabby-objects.tex
Fixed mathematical typo (thanks to the anonymous referee)
typo

\begin{proof}\begin{enumerate}
\item One can check that, for instance, the full powerset~$\P(X)$ and the set of
subterminals~$\P_{\leq 1}(X)$ are each injective.
\item The forgetful functor from modules to sets possesses a left exact left
adjoint. More explicitly, if~$i : A \to B$ is an injective map between sets and
if~$f : A \to I$ is an arbitrary map, then the induced map~$R\langle A \rangle
\to R\langle B \rangle$ between free modules is also injective, the given
map~$f$ lifts to a linear map~$R\langle A \rangle \to I$, and an~$R$-linear
extension~$R\langle B \rangle \to I$ induces an extension~$B \to I$ of~$f$.
\item One verifies that any abelian group embeds into a divisible
abelian group. By Baer's criterion (which requires the axiom of choice), divisible abelian groups are injective.
The result for modules over arbitrary rings then follows purely
formally, since the functor~$A \mapsto \Hom(R,A)$ from abelian groups
to~$R$-modules has a left exact left adjoint with monic unit. \qedhere
\end{enumerate}\end{proof}

@@

\begin{lemma}\label{lemma:notions-of-internal-injectivity}
Let~$Y$ be a ringed locale over a locale~$X$. Let~$I$ be a sheaf of modules over~$Y$.
Assuming Zorn's lemma in the metatheory, the following statements are equivalent:
\begin{enumerate}
\item $I$ is an injective sheaf of modules.
\item From the point of view of~$\Sh(Y)$, $I$ is an injective module.
\item From the point of view of~$\Sh(X)$, $I$ is an injective module from the
point of view of~$\Sh(I(Y))$.
\item From the point of view of~$\Sh(X)$, $I$ is an injective sheaf of modules
on~$I(Y)$.
\end{enumerate}
\end{lemma}

@@

The internal characterization provided by
Theorem~\ref{thm:higher-direct-images-as-internal-sheaf-cohomology} gives, as a
simple application, a logical explanation that higher direct images along
the identity~$\mathrm{id} : X \to X$ vanish: From the internal point of view
of~$\Sh(X)$, the over-locale~$X$ corresponds to the one-point locale, and the
higher cohomology of the one-point locale vanishes.

>>>>

\begin{proof}\begin{enumerate}
\item One can check that, for instance, the full powerset~$\P(X)$ and the set of
subterminals~$\P_{\leq 1}(X)$ are each injective.
\item The forgetful functor from modules to sets possesses a monomorphism-preserving left
adjoint. More explicitly, if~$i : A \to B$ is an injective map between sets and
if~$f : A \to I$ is an arbitrary map, then the induced map~$R\langle A \rangle
\to R\langle B \rangle$ between free modules is also injective, the given
map~$f$ lifts to a linear map~$R\langle A \rangle \to I$, and an~$R$-linear
extension~$R\langle B \rangle \to I$ induces an extension~$B \to I$ of~$f$.
\item One verifies that any abelian group embeds into a divisible
abelian group. By Baer's criterion (which requires the axiom of choice), divisible abelian groups are injective.
The result for modules over arbitrary rings then follows purely
formally, since the functor~$A \mapsto \Hom(R,A)$ from abelian groups
to~$R$-modules has a left exact left adjoint with monic unit. \qedhere
\end{enumerate}\end{proof}

@@

\begin{lemma}\label{lemma:notions-of-internal-injectivity}
Let~$Y$ be a ringed locale over a locale~$X$. Let~$J$ be a sheaf of modules over~$Y$.
Assuming Zorn's lemma in the metatheory, the following statements are equivalent:
\begin{enumerate}
\item $J$ is an injective sheaf of modules.
\item From the point of view of~$\Sh(Y)$, $J$ is an injective module.
\item From the point of view of~$\Sh(X)$, $J$ is an injective module from the
point of view of~$\Sh(I(Y))$.
\item From the point of view of~$\Sh(X)$, $J$ is an injective sheaf of modules
on~$I(Y)$.
\end{enumerate}
\end{lemma}

@@

The internal characterization provided by
Theorem~\ref{thm:higher-direct-images-as-internal-sheaf-cohomology} gives, as a
simple application, a logical explanation of the basic fact that higher direct images along
the identity~$\mathrm{id} : X \to X$ vanish: From the internal point of view
of~$\Sh(X)$, the over-locale~$X$ corresponds to the one-point locale, and the
higher cohomology of the one-point locale vanishes.
